---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r}
library(purrr)
library(tidyverse)
```


# hw07package

This package was created as a submission for Homework 07 requirement for STAT 547. It contains functions for performing a transformation of statistical data by the Box-Cox method.

## Installation

You can install the released version of hw07package from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("hw07package")
```

## Example

The primary function visible to the user is `boxcox`. Based on whether the first argument passed to the function is positive or negative, `boxcox` will use an appropriate internal function to calculate the Box-Cox transformation according to a specified lambda parameter (and lambda2 for a negative argument).

```{r example}
#positive argument
boxcox(10,2)

#negative argument
boxcox(-10, 2, 3)
```


```{r pressure, echo = FALSE}
sample_vec <- c(15, 16.3, 13.4, 17.8, 17.7, 27.1, 25, 19.5)
sample_boxcox <- map(sample_vec, boxcox, 2)
life <- as.numeric(gapminder$lifeExp)
sample_gap <- map(life, 3)
head(sample_gap)

library(gapminder)
hist(gapminder$lifeExp)
#hist(sample_gap)
```
