---
title: "Vignette for Box Cox Transformation"
author: "Bassam Javed"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette for Box Cox Transformation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The purpose of this vignette is to demonstrate the functions of this package, namely Box-Cox transformation.  

One of the foundations of statistics is the assumption of data distributed normally. However, in many real-life scenarios, this is not always the case. In order to make use of the statistical toolkit, non-normal data is often transformed by some known equation. One such transformation is to use take the logarithm of all data. In this package, I will demonstrate the use of the **Box-Cox family of transformations**:

*Positive data:*  
if $\lambda$ is not 0 then  
$x(\lambda) = (x^\lambda - 1)/\lambda$  
if $\lambda$ is 0, then $x(\lambda) = log(\lambda)$  
  
*Negative data:*  
if $\lambda_1$ is not 0, then $x(\lambda) = ((x+\lambda_2)^\lambda_1 - 1)/\lambda_1$  
if $\lambda_1$ is 0, then $x(\lambda) = log(x+\lambda_2)$

This package includes an .Rda file which contains an excerpt of data from the `gapminder` package. All values of life expectancy were extracted from `gapminder` into this package's 'gapminder_sample.Rda'.

```{r}
head(hw07package::gapminder_sample)
```

Let's compare a histogram of raw data to a histogram of data that has been transformed by this package's `boxcox` function.

```{r, fig.show='hold'}
gapminder_boxcox <- hw07package::boxcox(hw07package::gapminder_sample$lifeExp, 2)

hist(hw07package::gapminder_sample$lifeExp,
     breaks = 25, 
     main = "Raw data", 
     xlab = "Life expectancy")

hist(gapminder_boxcox, 
     breaks = 25, 
     main = "Box-Cox transformed",
     xlab = "Life expectancy (Box-Cox)")
```

### References:  
https://www.statisticshowto.datasciencecentral.com/box-cox-transformation/  
https://cran.r-project.org/web/packages/gapminder/gapminder.pdf
